CTCF threshold analysis

### 2022-07-04 07_CTCF_Threshold_mm.Rmd
Fix plotting

mtx_to_plot <- pivot_longer(gr_summary, cols = c("TP", "FP"), names_to = "Type")
ggplot(mtx_to_plot, aes(x = Threshold, y = value, color = Type)) +
  geom_line() +
  scale_x_continuous(breaks = thresholds, labels = scientific) +
  scale_y_continuous(breaks = seq(0, 1, 0.2))   + 
  scale_color_manual(values = mycols[1:2]) +
  coord_trans(x ="log10") +
  geom_vline(xintercept = 1E-6, linetype = "dashed", color = "black") +
  theme_bw() +
  theme(panel.grid.major = element_blank(), 
      panel.grid.minor = element_blank(), 
      # axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1),
      plot.title = element_text(hjust = 0.5),
      legend.text = element_text(size = 6)) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5, hjust=1)) +
  xlab("FIMO p-value threshold") +
  ylab("FP/TP rate")

ggsave(filename = fileNameOut1, width = 4.5, height = 1.5)
# dev.off()
# svg(filename = fileNameOut1, width = 7, height = 3)
# print(p)
# dev.off()

>>>>

mtx_to_plot <- pivot_longer(gr_summary, cols = c("TP", "FP"), names_to = "Type")
p <- ggplot(mtx_to_plot, aes(x = Threshold, y = value, color = Type)) +
  geom_line() +
  scale_x_continuous(breaks = thresholds, labels = scientific) +
  scale_y_continuous(breaks = seq(0, 1, 0.2))   + 
  scale_color_manual(values = mycols[1:2]) +
  coord_trans(x ="log10") +
  geom_vline(xintercept = 1E-6, linetype = "dashed", color = "black") +
  theme_bw() +
  theme(panel.grid.major = element_blank(), 
      panel.grid.minor = element_blank(), 
      # axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1),
      plot.title = element_text(hjust = 0.5),
      legend.text = element_text(size = 6)) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5, hjust=1)) +
  xlab("FIMO p-value threshold") +
  ylab("FP/TP rate")

# ggsave(filename = fileNameOut1, width = 4.5, height = 1.5)
dev.off()
svg(filename = fileNameOut1, width = 4.5, height = 1.5)
print(p)
dev.off()
